A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-30 paper.tex
3d N=8

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.  From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.

@@

\subsubsection{Topological A Twist}
\label{sect:3d8A_Twist}
From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.

@@

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}

>>>>

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.

@@

\begin{proof}
On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.  We can then enhance this identifying the fields, as $\ZZ$-graded $\mr U(1)$ with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.  When we calculate that dimensional reduction the fields reduce according to the rule
\begin{align*}
\Omega^{\bullet,\bullet}(\CC^2;\gg[k]) &\mapsto \Omega^{\bullet,\bullet}(\CC; \Omega^\bullet(\RR; \gg[k] \oplus \gg[k-1])) \\
&\iso \Omega^{0,\bullet}(\CC; \Omega^\bullet(\RR; (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]))).
\end{align*}
Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
\end{proof}

\subsubsection{Topological A Twist}
\label{sect:3d8A_Twist}
From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.

@@

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}
